Maenpuen et al. Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-05-13 ms/response_letter.Rmd

> Reviewer #1: Summary of Manuscript:
> This manuscript compares two methods of measuring LMA (leaf mass per area), an ecologically important functional trait in plants. It is a carefully executed and useful piece of work, in that LMA is a very widely measured plant trait and many readers will be interested in identifying the best methods to use when measuring LMA in their system, as well as how to compare their own measurements to other published estimates. However, I believe the paper needs modification; I include recommendations, including three major concerns, below:

We thank the reviewer for the encouraging comments and helpful critiques.

> 1. Framing: I think the paper misses an opportunity to provide a bit more context for why the study is important. The authors could provide more concrete examples of why standardizing LMA techniques across studies matters: e.g. what is the ecological significance of an LMA measurement difference between the two methods?  This could also be set up in the introduction by providing more context for LMA as a functional trait. For example, by citing the TRY database, the authors could provide readers with the importance and ubiquity of LMA relative to other plant traits (e.g. of all the studies of plant traits in TRY, how many report LMA?)

Thank you.
We now note that a key difference between leaf disc and whole-leaf LMA is that leaf disc LMA focuses on lamina rather than whole-leaf and usages depend on ecological contexts.
We also have mentioned the TRY database to explain LMA is the most often used leaf trait in TRY.

@@

> L101-102 again, might be worth stating why (even if it is discussed above)

Thank you.
We have repeated our expectations here.

> L107- 113 The description of the sites/data is a little confusing: it seems that there are two datasets: one which includes 3 different sites, and another that includes a fourth site, for which a subset of the samples had additional measurement taken. I recommend clarifying this section to explain the different levels of organization, as well as including some of the methodological data in Table S1 (e.g. number of total samples, whether leaf thickness was measured, leaf punch size).

Thank you.
We have added columns to explain the number of species, the number of individuals, whether leaf thickness was measured, and leaf punch size in Table S1.
We have also added detailed sampling protocol in Appendix S2.

@@

> L201-204 This is a result, and an important one (again, I'm thinking of readers who are looking for advice on how to measure LMA): it should be reported in the results section.

Thank you.
We have included this in the results section.

> L247 is this reported in the results somewhere? I thought the multiple discs/leaf were measured together?

Thank you.
That is not a result but an explanation.
Since we only measured 3 discs for each leaf in the Yunnan dataset, which is a common protocol, we cannot avoid the effect of variance within leaves.
We have updated the text.

@@

> Lines 26 and 51: Change "the key trait" to "an important functional trait".

Thank you.
We have updated the first one but keep the second one as "a key trait" because we have added the explanation on why LMA is considered as "a key trait" in the LES at the beginning of the introduction.

> Line 57: I think that the following reference helps to support this statement, because LMA values were found to vary across leaf age, and LMA also exhibits a plasticity to climate when leaves enter the maturation stage (Jiao et al., 2022).
> Jiao, Y., Niklas, K.J., Wang, L., Yu, K., Li, Y., Shi, P. 2022. Influence of leaf age on the scaling relationships of lamina biomass vs. area. Frontiers in Plant Science In press.

Thank you.
We have cited it in the context of "diminishing returns" in the discussion.

@@

> Lin, S., Shao, L., Hui, C., Song, Y., Reddy, G.V.P., Gielis, J., Li, F., Ding, Y., Wei, Q., Shi, P. 2018. Why does not the leaf weight-area allometry of bamboos follow the 3/2-power law? Frontiers in Plant Science 9: 583, https://doi.org/10.1016/10.3389/fpls.2018.00583

Thank you.
We originally had this result to support grouping species into four categories, because if the correlation between leaf area and leaf thickness are too strong, we cannot group species into four categories based on median values of traits.
As noted above, we removed the analysis of grouping species, and thus we also removed this result.

> Line 171: "… were 9.4% greater than disc-based estimates …" Can you provide a standard deviation or a confidence interval for 9.4%? In general, we can use the bootstrap method to get it.

Thank you.
We have added confidence intervals using bootstraps in the result section.

### 2022-05-13 ms/LMA_method.Rmd
update ms

# ABSTRACT

@@

**METHODS:**
We determined LMA using leaf discs and whole-leaf (including petiole) for `r val$all_sp` woody species from a wide range of biomes (tropics, subtropics, savanna, and temperate) to examine what extent whole-leaf and leaf disc LMA match, whether the differences in the estimates are associated with leaf size and thickness, and whether intraspecifc variation for each species match.

**RESULTS:**
Disc-based estimates of species and individual mean LMA matched well whole-leaf estimates.
Thin and large leaves had weaker correlations between leaf disc and whole-leaf estimates.
Variability of LMA estimates within species (i.e., amount of intraspecific variation) only weakly matched between whole-leaf and disc-based estimates (*R^2^* = `r val$cv_r2`).
We also found that sample with small total dry mass of leaf discs tended to show greater differences between leaf disc and whole-leaf LMA.

**CONCLUSIONS:**
Mean values of leaf disc LMA are generally good proxies for mean values of whole-leaf LMA with appropriate calibration (9.4% differences in our samples), but their accuracy depends on leaf size, leaf thickness, and sizes of leaf punch.
Therefore, using an appropriate size of leaf punch is important for obtaining stable estimates of leaf disc LMA that matches well with whole-leaf LMA.
Quantifying trait variation using leaf disc should be considered with caution.

@@

Intraspecific trait variation (ITV), which reflects both heritable genetic variation and phenotypic plasticity, influences plant responses to abiotic and biotic interactions [@Westerband2021].
The extent of ITV within and among communities for LMA can be similar to or greater than interspecific trait variation [e.g., @Messier2010; @Kichenin2013; @Fajardo2018].
The coefficient of variation (CV) is often used for quantifying the extent of ITV for each species [@Yang2020; @Westerband2021].
Sources of ITV for whole-leaf samples are variation among individuals within the same species and variation among leaves within the same individuals [@Messier2010; @Messier2017].
An additional source of trait variation for leaf disc samples is variation among leaf discs within the same leaves.
Given that leaf disc samples have more sources of ITV than whole-leaf samples, the effects of discrepancies between whole-leaf LMA and leaf disc LMA might be large when ITV is quantified based on CV.
Despite the importance of ITV in community ecology [@Siefert2015; @Westerband2021], the effect of different measurement methods on the extent of ITV has been largely ignored.

@@

Leaf disc LMA explained interspecific variations in whole-leaf LMA (*R^2^* = `r val$r2_lma`, *n* = `r val$all_sp`) quite well, and the strength of their relationship was approximately same or slightly weaker than previously reported  [*R^2^* = 0.92, *n* = 409, for whole-leaves in @Kraft2008; *R^2^* = 0.92, *n* = 364 for leaf laminas in @Onoda2011].
Standardized major axis (SMA) regression analysis showed significantly greater intercepts when all the species were pooled (9.4% differences).
Together, these findings suggest that disc-based estimates can be generally used as good proxies for their whole-leaf estimates with appropriate calibration
(
OLS regressions:
log~10~LMA~w~ = `r val$ols_int_log10` + `r val$ols_slope` $\times$ log~10~LMA~d~ or
log~10~LMA~d~ = `r val$ols_slope_inv` $\times$ log~10~LMA~w~,
where LMA~w~ and LMA~d~ are the whole-leaf and leaf disc LMA, respectively
).
However, leaf tissue density, leaf area, leaf thickness and leaf punch size also influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2 and Appendix SX).

The effect of leaf punch size was the most important source of the variation (Fig. 2, Appendix SX), and samples obtained with a small leaf punch showed greater variance in whole-leaf to leaf disc LMA ratio.
Small leaf disc size inflates trait variation within leaves because dry mass will be inflated when major veins are unintentionally included in the samples.
Species with lower leaf tissue density and thin leaves showed greater variance in whole-leaf to leaf disc LMA ratio especially when a small punch was used (Fig.2ac: small leaf punch, Fig. 2a: large leaf punch), suggesting that simple conversion between whole-leaf and leaf disc LMA is difficult for those species.
@Kraft2008 found high *R^2^* values (*R^2^* = 0.92) between whole-leaf and leaf disc LMA based on leaf discs of approximately 1.0-cm diameter for sapling leaves under closed canopy that are softer and thinner than adult leaves [@Kitajima2010; @Oktavia2020].
Altough a leaf punch of 1.0-cm diameter was used only in the Yakushima dataset in our study, the correlations were also strong for the Yakushima dataset, regardress of leaf tissue density or leaf thickness (Appendix SX).
The relatively low *R^2^* values for species with lower leaf tissue density and thin leaves in the Yunnan dataset (Appendix SX) compared to the previous study and the Yakushima dataset, may suggest not only the effect of distinct veins on variance in LMA [@John2017] or distinct veins with kite-type appearances [@Grubb1986] but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Appendices SX), and thus species with lower leaf tissue density and thin leaves, which have smaller dry mass (Appendix SX), tended to show grater variation in whole leaf to leaf disc LMA ratio especially when we used a smaller leaf punch.

Species with higher leaf tissue density and large leaves showed greater whole-leaf LMA than leaf disc LMA (Fig. 2ab: large leaf punch), suggesting that conversion between leaf disc and whole-leaf LMA should be possible using leaf area as a covariate (measuring leaf tissue density requires whole-leaf LMA itself).
We also observed that leaf disc and whole-leaf LMA estimate diverged for species with greater investment in petiole dry mass (Fig. 3a), and large-leaved species tended to have greater investment for petiole dry mass than small-leaved species (Fig. 3b).
This is consistent with the pattern of large leaves disproportionately investing in more leaf veins and/or petioles [@Niinemets2006; @Niinemets2007; @Sack2012] and the pattern of higher leaf tissue density associated with higher vein density [@John2017; @Sancho-Knapik2020] because those driving factors of LMA are likely to be ignored in leaf disc samples.
The estimated effects of leaf tissue density and leaf area was also positive for species obtained with a small leaf punch (Appdendix SX), but those effects were not significant.
This is probably because the variation in whole-leaf to leaf disc LMA ratio was too large to show clear effects of leaf tissue density and leaf area on the mean etimates ($\beta$ in Eq. 2) when a small leaf punch was used.

Even though we used the same species, the same individuals and the same trait (LMA) to estimate the extents of intraspecific trait variation (ITV), the explained variance of the relationship between whole-leaf and disc-based estimate was surprisingly small (Fig. 3; *R^2^* = `r val$cv_r2`).
This is probably because leaf disc samples have more sources of ITV than whole-leaf samples (i.e., variation among leaf discs within the same leaves).
On average, ITV based on leaf disc LMA was greater than ITV based on whole-leaf LMA.
Although there are not many studies that quantified trait variation within a single leaf, a previous study that used a giant leaved species *Alocasia macrorrhiza*, suggests that LMA varied within leaves due to reduced water supply and demand from midrib to outer regions [@Li2013a].
Because calculating the mean values generally diminishes the effect of within-sample variation, the relationship between disc-based estimates of individual mean LMA and its whole-leaf estimates will be stronger than the relationship between leaf disc CV and whole-leaf CV.
Thus, leaf disc and whole-leaf estimates of species means will show the strongest relationship.
The mismatch of ITV between whole-leaf and disc-based estimates could be ignored in the type of ITV studies that attempt to detemine sources of trait variation (e.g., site, across species, within species) which often use mixed linear modles and variance partitioning [e.g., @Messier2010; @Leps2011; @Siefert2015].
However, it is likely to change patterns significantly in the type of ITV studies that attempt to quantify the extent of ITV which usually use CV [i.g., @Albert2010a; @Bastias2017a; @Yang2020].
This caveat might apply to other leaf chemical traits such as leaf N contents because those traits have both disc and whole-leaf based estiamtes but those two estiamtes are usually not clarifeind in trait databases (e.g., TRY).
Since we used limited sample numbers (at least 5 samples per species) and most of them were obtained with a small punch, our study design may inflate errors in estimating ITV [@Yang2020].
Future studies should include more samples to improve the comparisons of leaf disc and whole-leaf based ITV.

The present study was designed to examine the extent to which whole leaf and leaf disc LMA matched.
Our study shows that mean values of leaf disc LMA is generally a good proxy for mean values of whole-leaf LMA.
However, larger and thinner leaves tended to show the large discrepancies between the leaf disc and whole-leaf estimates, and thus when one needs to mix leaf disc LMA and whole-leaf LMA in a single analysis (e.g., meta-analysis), appropriate calibrations are necessary.
Although our study was not designed to evaluate the effects of diameter sizes of leaf punches, the sizes of leaf punches are also the important sources of variance between whole-leaf and leaf disc LMA.
This is probably because small dry mass inflates measurement errors and small leaf disc size inflates trait variation within leave.
Additionally, although the mean values of leaf disc and whole-leaf LMA matched well, quantifying trait variation using leaf discs should be considered with caution, because variation among leaf discs within the same leaves (including measurement errors) seems to be large.
Leaf discs, which can target leaf lamina avoiding leaf veins, are useful and essential for biochemical determinations such as measurements of Rubisco activity [@Parry2002], because the photosynthetic activity occurs most in lamina rather than in veins for C~3~ plants [@Hibberd2002; @Gao2018].
Leaf disc LMA is also the preferred method for quantifying leaf lamina density, which avoid effects of veins.
However, if the objective is to use leaf disc LMA as an alternative for whole-leaf LMA, using an appropriate size of leaf punch is important for obtaining stable estimates of leaf disc LMA that matches well with whole-leaf LMA.

>>>>

# ABSTRACT (< 250 words, we need to remove 47 words!)

@@

**METHODS:**
We determined LMA using leaf discs and whole-leaf (including petiole) for `r val$all_sp` woody species from a wide range of biomes (tropics, subtropics, savanna, and temperate) to examine what extent whole-leaf and leaf disc LMA match,
whether the relationship varied with leaf tissue density, leaf area, leaf thickness and leaf punch size (0.6-cm and 1.0-cm in diameter),
and whether the extent of intraspecifc variation (ITV) for each species matches.

**RESULTS:**
Disc-based estimates of species mean LMA matched well whole-leaf estimates, and whole-leaf LMA tended to be higher than leaf disc LMA.
The whole-leaf to leaf disc LMA ratio was higher for species with higher leaf tissue density and larger leaf, and their variance was greater for species with lower leaf tissue density and thinner leaves.
Small leaf punch also inflated the whole-leaf to leaf disc LMA ratio.
Variability of LMA estimates within species (i.e., extent of ITV) only weakly matched between whole-leaf and disc-based estimates (*R^2^* = `r val$cv_r2`).

**CONCLUSIONS:**
Mean values of leaf disc LMA are generally good proxies for mean values of whole-leaf LMA with appropriate calibration (`r val$sma_per_all_mean`% differences in our samples), but their accuracy depends on leaf morphology, and sizes of leaf punch.
Our results suggest that simple conversion between whole-leaf and leaf disc LMA is difficult for species obtained with a small leaf punch.
Accurately representing leaf traits will probably require careful selection between leaf disc and whole-leaf traits depending on the objectives.
Quantifying trait variation using leaf disc should be also considered with caution.

@@

Intraspecific trait variation (ITV), which reflects both heritable genetic variation and phenotypic plasticity, influences plant responses to abiotic and biotic interactions [@Westerband2021].
For example, shade leaves tend to have lower LMA than sun leaves because of fewer layers of palisade mesophyll cells [@Terashima2001; @Onoda2008].
The extent of ITV within and among communities for LMA can be similar to or greater than interspecific trait variation [e.g., @Messier2010; @Kichenin2013; @Fajardo2018].
The coefficient of variation (CV) is often used for quantifying the extent of ITV for each species [@Yang2020; @Westerband2021].
Sources of ITV for whole-leaf samples are variation among individuals within the same species and variation among leaves within the same individuals [@Messier2010; @Messier2017].
An additional source of trait variation for leaf disc samples is variation among leaf discs within the same leaves.
Given that leaf disc samples have more sources of ITV than whole-leaf samples, the effects of discrepancies between whole-leaf LMA and leaf disc LMA might be large when ITV is quantified based on CV.
Despite the importance of ITV in community ecology [@Siefert2015; @Westerband2021], the effect of different measurement methods on the extent of ITV has been largely ignored.

@@

Leaf disc LMA explained interspecific variations in whole-leaf LMA (*R^2^* = `r val$r2_lma`, *n* = `r val$all_sp`) quite well, and the strength of their relationship was approximately same or slightly weaker than previously reported  [*R^2^* = 0.92, *n* = 409, for whole-leaves in @Kraft2008; *R^2^* = 0.92, *n* = 364 for leaf laminas in @Onoda2011].
Standardized major axis (SMA) regression analysis showed significantly greater intercepts when all the species were pooled (9.4% differences).
Together, these findings suggest that disc-based estimates can be generally used as good proxies for their whole-leaf estimates with appropriate calibration (see discussion below).
However, leaf tissue density, leaf area, leaf thickness and leaf punch size also influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2 and Appendix SX).

*Effects of leaf punch size and leaf morphology*

The effect of leaf punch size was the most important source of the variation (Fig. 2, Appendix SX), and samples obtained with a small leaf punch showed greater variance in whole-leaf to leaf disc LMA ratio.
Small leaf disc size inflates trait varition within leaves because dry mass will be inflated when major veins are unintentionally included in the samples.
Species with lower leaf tissue density and thin leaves showed greater variance in whole-leaf to leaf disc LMA ratio especially when a small punch was used (Fig.2ac: small leaf punch, Fig. 2a: large leaf punch).
@Kraft2008 found high *R^2^* values (*R^2^* = 0.92) between whole-leaf and leaf disc LMA based on leaf discs of approximately 1.0-cm diameter for sapling leaves under closed canopy that are softer and thinner than adult leaves [@Kitajima2010; @Oktavia2020].
Altough a leaf punch of 1.0-cm diameter was used only in the Yakushima dataset in our study, the correlations were also strong for the Yakushima dataset, regardress of leaf tissue density or leaf thickness (Appendix SX).
On the other hand, a previous study found that leaf disc LMA obtained with a very small leaf punch (0.3-cm diameter) and whole-leaf LMA had different relationships between shade tolerance [@Poorter2009a], suggesting that leaf disc LMA and whole-leaf LMA can be inheretly different when small disc samples were used.
The relatively low *R^2^* values in the Yunnan dataset (Appendix SX) compared to the previous study and the Yakushima dataset may suggest not only the effect of distinct veins on variance in LMA [@John2017] or distinct veins with kite-type appearances [@Grubb1986] but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Appendix SX), and thus species with lower leaf tissue density and thin leaves, which have smaller dry mass (Appendix SX), tended to show grater variation in whole leaf to leaf disc LMA ratio especially when we used a smaller leaf punch.

Species with higher leaf tissue density and large leaves showed greater whole-leaf LMA than leaf disc LMA (Fig. 2ab: large leaf punch).
We also observed that leaf disc and whole-leaf LMA estimate diverged for species with greater investment in petiole dry mass (Fig. 3a), and large-leaved species tended to have greater investment for petiole dry mass than small-leaved species (Fig. 3b).
This is consistent with the pattern of large leaves disproportionately investing in more leaf veins and/or petioles [@Niinemets2006; @Niinemets2007; @Sack2012] and the pattern of higher leaf tissue density associated with higher vein density [@John2017; @Sancho-Knapik2020] because those driving factors of LMA are likely to be ignored in leaf disc samples.
The estimated effects of leaf tissue density and leaf area was also positive for species obtained with a small leaf punch (Appdendix SX), but those effects were not significant.
This is probably because the variation in whole-leaf to leaf disc LMA ratio was too large to show clear effects of leaf tissue density and leaf area on the mean etimates ($\beta$ in Eq. 2) when a small leaf punch was used.

*Conversion between whole-leaf and leaf disc LMA*

When the objective is to use leaf disc LMA as an alternative for whole-leaf LMA, using an appropriate size of leaf punch (e.g., 1.0-cm in diameter) is important for obtaining stable estimates of leaf disc LMA that matches well with whole-leaf LMA.
Our results suggest that simple conversion between whole-leaf and leaf disc LMA is difficult for species obtained with a small leaf punch.
The effects of leaf tissue density and leaf area are predictable when we used a large leaf punch (Fig. 2ab: large leaf punch), suggesting that conversion between leaf disc and whole-leaf LMA should be possible using leaf area as a covariate (measuring leaf tissue density requires whole-leaf LMA itself).
OLS regressions with leaf area as a covariate as follwoing:
(1) log~10~LMA~w~ = `r val$yaku2_slope_disc` $\times$ log~10~LMA~d~ + `r val$yaku2_slope_area` $\times$ log~10~LA,
(2) log~10~LMA~d~ = `r val$yaku2_int_inv_log10` + `r val$yaku2_slope_inv_leaf` $\times$ log~10~LMA~w~  - 0.063  $\times$ log~10~LA (*R^2^* = `r val$yaku_r2_area`, *AIC* = `r val$yaku_aic_area`, *n* = `r val$yaku_sp`),
where LMA~w~, LMA~d~, and LA are the whole-leaf LMA, leaf disc LMA and leaf area, respectively.
OLS regressions without leaf area as a covariate as follwoing:
(3) log~10~LMA~w~ = `r val$yaku_int_log10` + `r val$yaku_slope_disc` $\times$ log~10~LMA~d~ or
(4) log~10~LMA~d~ = `r val$yaku_slope_inv_leaf` $\times$ log~10~LMA~w~
(*R^2^* = `r val$yaku_r2_simple`, *AIC* = `r val$yaku_aic_simple`, *n* = `r val$yaku_sp`).
Nonetheless, including leaf area only slighlty imporves the *R^2^* values for the Yakushima dataset where a large punch was used.
This is because the large descripancy in the whole-leaf to leaf disc LMA for large leaves can be explained by scaling relationships between leaf mass and leaf area called "dimishing returns" [@Niklas2007] which refers to increases in leaf dry mass including petioles do not result in the proportional increase in leaf area including petioles [@Li2022], which is strong for mature leaves [@Jiao2022].
The "dimishing returns" can be either descirbed as the scaling slope of leaf area in the model 1 or the scaling slope of leaf-disc LMA and the intercept in the model 3.
When one needs to mix leaf disc LMA and whole-leaf LMA in a single analysis (e.g., meta-analysis) or quickly measure leaf disc LMA as a proxy for whole-leaf LMA, we recommend to covert LMA values using one of the models above.

*Intraspecific variation*

Even though we used the same species, the same individuals and the same trait (LMA) to estimate the extents of intraspecific trait variation (ITV), the explained variance of the relationship between whole-leaf and disc-based estimate was surprisingly small (Fig. 3; *R^2^* = `r val$cv_r2`).
This is probably because leaf disc samples have more sources of ITV than whole-leaf samples (i.e., variation among leaf discs within the same leaves).
On average, ITV based on leaf disc LMA was greater than ITV based on whole-leaf LMA as we expected.
Although there are not many studies that quantified trait variation within a single leaf, a previous study that used a giant leaved species *Alocasia macrorrhiza*, suggests that LMA varied within leaves due to reduced water supply and demand from midrib to outer regions [@Li2013a].
Because calculating the mean values generally diminishes the effect of within-sample variation, the relationship between disc-based estimates of individual mean LMA and its whole-leaf estimates will be stronger than the relationship between leaf disc CV and whole-leaf CV.
Thus, leaf disc and whole-leaf estimates of species means will show the strongest relationship.
The mismatch of ITV between whole-leaf and disc-based estimates could be ignored in the type of ITV studies that attempt to detemine sources of trait variation (e.g., site, across species, within species) which often use mixed linear modles and variance partitioning [e.g., @Messier2010; @Leps2011; @Siefert2015].
However, it is likely to change patterns significantly in the type of ITV studies that attempt to quantify the extent of ITV which usually use CV [i.g., @Albert2010a; @Bastias2017a; @Yang2020].
This caveat might apply to other leaf chemical traits such as leaf N contents because those traits have both disc and whole-leaf based estimates but those two estimates are usually not clarifeind in trait databases (e.g., TRY).
Since we used limited sample numbers (at least 5 samples per species) and most of them were obtained with a small punch, our study design may inflate errors in estimating ITV [@Yang2020].
Future studies should include more samples to improve the comparisons of leaf disc and whole-leaf based ITV.

*Conclusions*

The present study was designed to examine the extent to which whole leaf and leaf disc LMA matched.
Although our study was not designed to evaluate the effects of diameter sizes of leaf punches, the sizes of leaf punches as well as leaf morphology are the important sources of variance between whole-leaf and leaf disc LMA.
Our study shows that mean values of leaf disc LMA is generally a good proxy for mean values of whole-leaf LMA when an appropriate size of leaf punch (e.g., 1.0-cm in diameter) was used.
Thhose LMA values can be converted using OLS regressions.
Additionally, although the mean values of leaf disc and whole-leaf LMA matched well, quantifying trait variation using leaf discs should be considered with caution, because variation among leaf discs within the same leaves (including measurement errors) seems to be considerably large but cannot be avoid for typical sampling numbers (2-3 discs per leaf).
Leaf discs, which can target leaf lamina avoiding leaf veins, are useful and essential for biochemical determinations such as measurements of Rubisco activity [@Parry2002], because the photosynthetic activity occurs most in lamina rather than in veins for C~3~ plants [@Hibberd2002; @Gao2018].
Leaf disc LMA is also the preferred method for quantifying leaf lamina density, which avoid effects of veins.
Accurately representing leaf traits will probably require careful selection between leaf disc and whole-leaf traits depending on the objectives.
